Thoughts on resubmission within ARC1

### 2009-03-20 doc/client/client_technical.tex
Update migration and resubmission part

The \texttt{Migrate} method behaves in much the same way as the \texttt{Submit}
method, but instead of sending a new job request to the cluster it sends a 
migration request of a given job, currently this request is only supported 
for ARC1 clusters. The \texttt{url} and \texttt{jobdesc} specifies the job-id 
and {\JobDescription} of the job which should be migrated.\\
The migration request will create a new job where the local input files are 
transferred from old cluster. Once the input files have been transferred the 
new cluster will send a request to kill the old job. If the kill request is 
unsuccessful the new job will be terminated unless the \texttt{forcemigration} 
boolean is \texttt{true}.\\
The \texttt{Migrate} method will also fill the \texttt{info} {\XMLNode} with 
information about the job the same way as the \texttt{Submit} method. However 
for the \texttt{Migrate} method this \texttt{XMLNode} also contain the job-id 
of the migrated job.

@@

The other public methods of the {\JobController} class are:
The \texttt{Get} which is used to download jobs
\begin{shaded}
\begin{verbatim}
bool Get(const std::list<std::string>& status, const std::string& downloaddir,
         const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Kill(const std::list<std::string>& status, const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Clean(const std::list<std::string>& status, const bool force, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Cat(const std::list<std::string>& status, const std::string& whichfile, 
         const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool RemoveJobs(const std::list<URL>& jobids);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
std::list<std::string> GetDownloadFiles(const URL& dir);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool CopyFile(const URL& src, const URL& dst);
\end{verbatim}
\end{shaded}
The \texttt{GetJobDescriptions} method 
\begin{shaded}
\begin{verbatim}
std::list<Job> GetJobDescriptions(const std::list<std::string>& status, 
                                  const bool getlocal, const int timeout);
\end{verbatim}
\end{shaded}
which is used to get the job descriptions of {\Job}s in the \texttt{JobStore} 
with the specified status'. In case \texttt{getlocal} is true the job description 
will first be searched for the users local XML file. If a local copy of 
the job description is found the checksum of the local input files will be 
computed and compared with the ones listed in the users local XML file. If 
all checksums match the job description is returned.\\
In case \texttt{getlocal} is false or the retrieval of the local job description 
fails the job description will be tried retrieved from the cluster. This has 
currently only been implemented for ARC(both generations) clusters. Note 
that the job descriptions retried from a cluster might will most likely have 
been changed since the submission either by the cluster\footnote{For both 
generations of ARC it is possible to recover the initial job description send 
to the cluster. However modifications can still have been made to the 
job description before sending it to the cluster.} or by the submission 
client. Therefore the only way of retrieving the original job description is 
through the users local XML file.\\
The \texttt{GetJobDescriptions} returns a list of the  {\Job}s where job description 
have been found. The found job descriptions are kept in the 
{\Job}.\texttt{JobDescription} attribute.

The \texttt{Migrate} method:
\begin{shaded}
\begin{verbatim}
bool Migrate(TargetGenerator& targetGen,
             Broker* broker,
             const bool forcemigration,
             const int timeout);
\end{verbatim}
\end{shaded}
will try to migrate the jobs contained in the object ({\JobController}). The jobs
will be migrated to the targets specified in {\TargetGenerator} \texttt{targetGen}
by using the broker specified by {\Broker} \texttt{broker}. The boolean
\texttt{forcemigration} specifies whether a migrated job should persist if the
new cluster ({\ExecutionTarget}) chosen by the {\TargetGenerator} does not
succeed sending a kill/terminate request for the job. The integer
\texttt{timeout} argument has not yet been implemented.

@@

Given all components listed above it is possible to write versatile
command line interfaces (cli) for grid job submission and
management. {\libarcclient} offers the following native commands:

\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status
  queries.}
\item{\texttt{arcsub} - for grid job submission.}
\item{\texttt{arcget} - for downloading output of finished, cancelled
  or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory
  including all contents.}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a
  running grid job's std out or std error file.}
\item{\texttt{arcsync} - for synchronising the information in the user's
  local XML file about active jobs.}
\item{\texttt{arcresub} - for redoing an entire job on the same or a new
  computing resource.}
\item{\texttt{arcmigrate} - for moving a queuing job from an ARC1 
  computing resource to another.}
\end{enumerate}

>>>>

The \texttt{Migrate} method behaves in much the same way as the \texttt{Submit}
method, but instead of sending a new job request to the cluster it sends a 
migration request of a given job, currently this request is only supported 
for ARC1 clusters. The \texttt{URL} and \texttt{jobdesc} specifies the job-id 
and {\JobDescription} of the job which should be migrated.

Note that whereas the \texttt{Migrate} method make provisions for automatically 
getting files from the migration source cluster, this does not apply to the job 
description which instead should be passed to \texttt{Migrate} explicitly in the 
form of a {\JobDescription} object.

The migration request will create a new job where the local input files are 
transferred from old cluster. Once the input files have been transferred the 
new cluster will send a request to kill the old job. If the kill request is 
unsuccessful the new job will be terminated unless the \texttt{forcemigration} 
boolean is \texttt{true}.

The \texttt{Migrate} method will also fill the \texttt{info} {\XMLNode} with 
information about the job the same way as the \texttt{Submit} method. However 
for the \texttt{Migrate} method this \texttt{XMLNode} also contain the job-id 
of the migrated job.

@@

The other public methods of the {\JobController} class are:
The \texttt{Get} which is used to download jobs
\begin{shaded}
\begin{verbatim}
bool Get(const std::list<std::string>& status, const std::string& downloaddir,
         const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Kill(const std::list<std::string>& status, const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Clean(const std::list<std::string>& status, const bool force, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Cat(const std::list<std::string>& status, const std::string& whichfile, 
         const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool RemoveJobs(const std::list<URL>& jobids);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
std::list<std::string> GetDownloadFiles(const URL& dir);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool CopyFile(const URL& src, const URL& dst);
\end{verbatim}
\end{shaded}
The \texttt{GetJobDescriptions} method 
\begin{shaded}
\begin{verbatim}
std::list<Job> GetJobDescriptions(const std::list<std::string>& status, 
                                  const bool getlocal, const int timeout);
\end{verbatim}
\end{shaded}
which is used to get the job descriptions of {\Job}s in the \texttt{JobStore} 
with the specified status'. In case \texttt{getlocal} is true the job description 
will first be searched for the users local XML file. If a local copy of 
the job description is found the checksum of the local input files will be 
computed and compared with the ones listed in the users local XML file. If 
all checksums match the job description is returned.

In case \texttt{getlocal} is false or the retrieval of the local job description 
fails an attempt will be made to retrieved the job description from the cluster. This has 
currently only been implemented for ARC(both generations) clusters. Note 
that the job descriptions retrieved from a cluster will most likely have 
been changed since the submission -- either by the cluster\footnote{For both 
generations of ARC it is possible to recover the initial job description send 
to the cluster. However modifications can still have been made to the 
job description before sending it to the cluster.} or by the submission 
client. Therefore, the only way of retrieving the original job description is 
through the users local XML file.

The \texttt{GetJobDescriptions} returns a list of the  {\Job}s where job description 
have been found. The found job descriptions are kept in the 
{\Job}.\texttt{JobDescription} attribute.

The \texttt{Migrate} method
\begin{shaded}
\begin{verbatim}
bool Migrate(TargetGenerator& targetGen,
             Broker* broker,
             const bool forcemigration,
             const int timeout);
\end{verbatim}
\end{shaded}
will try to migrate the jobs contained in the object ({\JobController}). The jobs
will be migrated to the targets specified in {\TargetGenerator} \texttt{targetGen}
by using the broker specified by {\Broker} \texttt{broker}. The boolean
\texttt{forcemigration} specifies whether a migrated job should persist if the
new cluster ({\ExecutionTarget}) chosen by the {\TargetGenerator} does not
succeed sending a kill/terminate request for the job. The integer
\texttt{timeout} argument has not yet been implemented.

@@

Given all components listed above it is possible to write versatile
command line interfaces (cli) for grid job submission and
management. {\libarcclient} offers the following native commands:
\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status 
queries.}
\item{\texttt{arcsub} - for grid job submission.}
\item{\texttt{arcget} - for downloading output of finished, cancelled 
or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory 
including all contents.}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a 
running grid job's std out or std error file.}
\item{\texttt{arcsync} - for synchronising the information in the user's 
local XML file\footnote{By default \$HOME/.arc/jobs.xml} about active jobs.}
\item{\texttt{arcresub} - for starting an entire job over on either the 
same or a new computing resource.}
\item{\texttt{arcmigrate} - for moving a queuing job from one A-REX 
server to another.}
\end{enumerate}
